Goes Here

### 2012-07-30 paper.tex
code example

\subsection{Search Space Reduction and Optimization}
Describe four main components and some built-in libraries.
In our
framework, we propose an optimization component that

@@

has $N^M$ dimensions. To overcome this problem, we reduce

@@

same time not to prune out good solutions. The reduced
space allows for the use of standard optimization techniques such as simulated annealing, genetic algorithms,
Markov Chain Monte Carlo methods, and even an exhaustive search. The low-dimensional space produced by the

@@

\subsection{Simulation}
Another key step in the process of converting abstractions to physical output is being able to
simulate what an output device is going to generate given a well-defined input. 
A simulation allows the user to preview how the output will look and behave. 
This simulation is a generalization of the print-preview function
available in word processing applications.
As physical output generation might be costly or time-consuming, 
it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
That means that the simulation must accurately predict the output. 
It's necessary to develop very efficient and accurate rendering
and finite element simulation packages. Since we run the simulation multiple times within the optimization method
we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
\section{Programming with Our API}

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.

>>>>

\subsection{Search Space Decomposition and Reduction}
Our framework includes an optimization component that

@@

has $N^M$ dimensions. To overcome this problem, we decompose the search
space into similar subproblems and also reduce

@@

same time not to prune out good solutions. The low-dimensional space produced by the

@@

\section{Optimization}
Our optimization component is an interface to 
existing standard optimization techniques
such as simulated annealing, genetic algorithms and
Markov Chain Monte Carlo methods, as well as custom optimization algorithms implemented
by more advanced users.
\subsection{Simulation}
Another key step in the process of converting abstractions to physical output is being able to
simulate what an output device is going to generate given a well-defined input. 
A simulation allows the user to preview how the output will look and behave. 
This simulation is a generalization of the print-preview function
available in word processing applications.
As physical output generation might be costly or time-consuming, 
it is extremely beneficial for users to be able to preview the output and make immediate changes to the design.
That means that the simulation must accurately predict the output. 
It's necessary to develop very efficient and accurate rendering
and finite element simulation packages. Since we run the simulation multiple times within the optimization method
we can cache and reuse partial simulation results, speeding up the evaluation process at least 10-100 times.
Furthermore, we will ensure that the simulation is accurate by measuring properties of the printing materials and using
these measurements to estimate the parameters of data-driven material models (e.g., for elasticity, reflectance).
\section{Programming with Our API}
Code examples:
To generate textured model:
\begin{verbatim}
Manager manager;
manager.loadMaterialLibrary("material_file");
manager.setGenerator(new HeightFieldGenerator());
manager.setSimulator(new SomeColorSimulator());
manager.setMetric(new SomeColorMetric());
manager.setOptimizer(
  new SimulatedAnealing/GradientDescent());
Objective obj;
Scene scene;
TexturedShape shape("filename"), goal("filename1");
scene.addShape(shape);
obj.setScene(scene);
obj.setGoal(goal);
manager.addObjective(obj);
\end{verbatim}

To generate BRDF
\begin{verbatim}
manager.setGenerator(new StackingGenerator());
manager.setSimulator(new BRDFSimulator());
manager.setMetric(new SomeImageMetric());
Shape shape("filename"), 
Image goal("filename1");
\end{verbatim}

Deformation
\begin{verbatim}
scene.addForce(new Force(pos, dir, shapeID));
scene.addConstraint(
  new Constraint(FIX_VERTEX, vertexList, shapeID));
Shape goal;
manager.setSimulator(new FEMSimulator());
\end{verbatim}
\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.
